---
title: "Alcohol vs Seat choice"
author: "Logan DeHay"
date: "Fall 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  The median for alcohol consumption of those who sit in the rear is dramatically greater than the median of those who sit in the front, and middle (median of 5 as opposed to median of 1, and 0 respectively). The data indicates a bias in which those who sit in the back drink more alcohol than those who sit in the front and middle. 
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

  The standard deviation of the date for those who sit in the back, is much greater than that of those who sit in the front or middle. The boxplot has distinct notches which vary from a conventional boxplot: these notches are indications of the standard deviation. The widely differing standard deviations indicate that the alcohol consumption of those who sit in the back varies much more than the data for the other locations. The median, and other characteristics of data are the same of the previous boxplot.
  
## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
The numerical data affirms the previous two boxplots. The students siting in the front drink an average of 1.7875 tims a week, students in the middle an average of 3.331461 times a week, and students in the back an average of 8.555... times a week. These demonstrate an increase in drinks from front to back. The standard deviation of those who sit in the back is 12.58 which dwarfs the other standard deviations of 3.8, and 6.22 for the front and middle. The variety in alcohol consumption increases from front to back, and the mean follows a similar trend.

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The p-value is 0.000116 indicating that the probability of these results occurring naturally without any influence or bias is 0.116%. Such a p-value means that there are at least two rows in which the alcohol consumption is significantly different.

```{r}
plot(TukeyHSD(model1))
```
  
According to the differences in mean levels, the back is drinking 12 to 4 more drinks than the front is. The back is drinking around 10 to 3 more drinks than the middle. The difference between the middle and front is nothing because the zero mark is inside the confidence level of the difference.

## Conclusions

The problem was found to be a numerical~categorical problem. This incited me to upload the numerical~cat.rmd file. After looking at the various forms of data (boxplot, fancy boxplot, etc.), the obvious bias derived was that the back row significantly drank more than the the middle and front according to the mean average and deviation. Our p-value was significant and using a Tukey HSD test, we determined that the back row drank substantially more.
